---
title: "ENV S 193DS Homework 3"
date: 2024-05-31
author: "Aidan Robertson
format: pdf
---

## [Forked repository](https://github.com/aidan-robertson/robertson_aidan_homework-03)

# Set-up

## reading in data & packages

```{r}
#| message: false
# general use
library(tidyverse)
library(readxl)
library(here)
library(janitor)

# visualizing pairs
library(GGally)

# model selection
library(MuMIn)

# model predictions
library(ggeffects)

# model tables
library(gtsummary)
library(flextable)
library(modelsummary)
```

# Problem 1. Multiple linear regression: model selection & construction

## a. table of models
```{r}
modelsummary::modelsummary( # list of all models (null, saturated, sla/water treatment, sla/species, species/water treatment)
  list( 
    "null" = model0,
    "model 1" = model1,
    "model 2" = model2,
    "model 3" = model3,
    "model 4" = model4),
  output = "flextable", # display as flextable
  gof_omit = "^(?!.*IC)") # keep only AIC and BIC statistics
```

## b. statistical methods


## c. best model visualization

## d. caption

## e. results

# Problem 2. Affective visualization

## a. description of an aggective visualization

## b. sketch of idea

## c. draft of visualization

## d. artist statement

## Problem 3. Statistical critique

## a. revisit and summarize

## b. visual clarity

## c. aesthetic clarity

## d. recommendations
