---
title: "ENV S 193DS Homework 3"
date: 2024-05-31
author: "Aidan Robertson
format: pdf
---

## [Forked repository](https://github.com/aidan-robertson/robertson_aidan_homework-03)

# Set-up

## reading in data & packages

```{r}
#| message: false
# general use
library(tidyverse)
library(readxl)
library(here)
library(janitor)

# visualizing pairs
library(GGally)

# model selection
library(MuMIn)

# model predictions
library(ggeffects)

# model tables
library(gtsummary)
library(flextable)
library(modelsummary)
```

# Problem 1. Multiple linear regression: model selection & construction

## a. table of models
```{r}
modelsummary::modelsummary( # list of all models (null, saturated, sla/water treatment, sla/species, species/water treatment)
  list( 
    "null" = model0,
    "model 1" = model1,
    "model 2" = model2,
    "model 3" = model3,
    "model 4" = model4),
  output = "flextable", # display as flextable
  gof_omit = "^(?!.*IC)") # keep only AIC and BIC statistics
```

## b. statistical methods
In exploring how to best predict total biomass of plants, I created 5 linear models with different combinations of potential influential variables - specific leaf area (sla), water treatment, and species. To determine the model that best described total plant biomass, I first created models for each combination of variables (none, all, sla-water treatment, sla-species, and species-water treatment) and then compared the models using the Akaike Information Criterion (AIC) to determine which had the closest fit to the data. The model with the lowest reported AIC was one that used species and water treatment to predict plant biomass. To make sure this model conformed to linear model assumptions, I looked at it's diagnostics

## c. best model visualization

## d. caption

## e. results

# Problem 2. Affective visualization

## a. description of an aggective visualization

## b. sketch of idea

## c. draft of visualization

## d. artist statement

## Problem 3. Statistical critique

## a. revisit and summarize

## b. visual clarity

## c. aesthetic clarity

## d. recommendations
